% 英文摘要
With the rapid advancement of remote sensing technology, we now can acquire a wealth of high-resolution (HR) and low-resolution (LR) remote sensing image resources. HR images can provide rich detail information, but they are limited by cost and continuity constraints. On the other hand, easily obtainable and cost-effective LR images hold great potential for application. However, effectively extracting subtle and non-intuitively recognizable information from LR images poses a significant challenge. Addressing this issue, this paper designs and implements an attention mechanism-based deep learning U-Net model on the CRVC cross-resolution vehicle counting dataset, aiming to fully leverage the implicit spatial and temporal information in remote sensing images to enhance the accuracy of object counting.

This study analyzes the spatial consistency and temporal continuity between HR and LR images within the CRVC dataset and introduces targeted processing through a temporal attention module and a cross-resolution attention module. The research demonstrates the potential of attention mechanisms to boost model performance, particularly in enhancing the model's ability to synthesize diverse feature representations. By comparing with leading counting methods and further optimizing the algorithm through ablation studies, our model shows significant improvements in vehicle counting accuracy and model generalization ability. The research findings presented in this paper are not only valuable for the field of vehicle counting but also exhibit considerable potential for broader applications such as smart city design. 